Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-13 Paper/ms.tex
Commas

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: $P_i$, the orbital period, $A_i$, the amplitude (in metres
per second) of the RV signal, $\phi_i$, the phase of the signal, $e_i$, the eccentricity of the orbit, and $\theta_i$, a ``viewing angle'' parameter
describing the position of the observer with respect to the major axis of the
star's elliptical trajectory.

@@

The prior for the velocity amplitudes $A_i$ is important and will affect the
inferred number of planets $N$. For example, if the prior allows for very
low amplitude planets to exist, the data will not rule this out. The prior
will influence how many of these low amplitude planets will exist: if we
believe there are many, and the data are uninformative about low amplitude
planets, then the posterior distribution for $N$ will also indicate that there
may be many low amplitude planets. However, their other properties, such as
their orbital periods, will not be well determined.

>>>>

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: the orbital period $P_i$, the semi-amplitude (in metres
per second) of the RV signal $A_i$, the phase of the signal
$\phi_i$, the eccentricity $e_i$, and the ``viewing angle'' $\theta_i$.

@@

The prior for the velocity semi-amplitudes $\{A_i\}$ is important and will affect the
inferred number of planets $N$. For example, if the prior allows for very
low amplitude planets to exist, the data will not rule this out, and the posterior
for $N$ will include the possibility of large numbers of planets. The prior
will influence how many of these low amplitude planets will exist: if we
believe there are many, and the data are uninformative about low amplitude
planets, then the posterior distribution for $N$ will also indicate that there
may be many low amplitude planets. However, their other properties, such as
their orbital periods, will not be well determined.
